NIRCam Faint and Bright Flux Calibration Plan

### 2017-04-24 ms.tex
finished figure cap of faint white dwarf network stars.
I revised the discussion of NIRCam frame timing issues after discussing with Jarron.

\subsection{Hectospec Observations}
We observed NGC~2420 with two fiber configurations in the Spring and Fall of 2016.
We used the 600 gpm grating (1.9 - 2.2 $\AA$ resolution element) to match with existing spectral template libraries with 3.6 $\AA$ resolution.
We selected the central wavelength to be 4800 $\AA$ which means that the wavelength coverage is about 3550 to 6050 $\AA$, which covers several import criteria for G-star classification many of which are concentrated between 4000 and 4400 $\AA$.
We obtained exposure times of 1.7 hours (Spring 2016) and 2 hours (Fall 2016).
The minimum fiber separation $\sim$20$\arcsec$ required that we observe in two configurations to increase the density of stars for which we had spectral classification.
During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for fixing and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).

@@

We normalized the raw spectra output from \texttt{HSRED} in order to pass it to a spectral rectification program \texttt{mkclass} \citep{gray2014classification}.
The first step in the normalization was to get an approximately normalized curve from the strongly curved spectrum shown in Figure \ref{fig:SpecRect}.
We fit an 8th order polynomial in log space to the flux as a function of wavelength.
It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the best-fit polynomial drops to low values and the fit can have zero crossings.
If this polynomial model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings and reduced systematics at low fluxes.
The polynomial fit is done piecewise in 3 equally spaced regions to take on small scale curvature.

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{calspec_and_new_clust_wd.pdf}
\caption{The NIRCam saturation and sensitivities are shown as in Figure \ref{fig:JWSTcalsWideF}.
This time, we show the CALSPEC stars, G2~V open cluster stars and placeholder spectra for WD stars from \citet{narayan2016wdnetwork}.
The faint WD stars .}\label{fig:wideFiltWDCalspec}
\end{figure}

@@

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the MSX calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Survey Experiment (MSX) calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).

@@

\begin{table}[!b]
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:conversionSteps}
\begin{tabular}{lrrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& $K_\mathrm{src}$		& ND Square		& Subarray	& Filter & t$_\mathrm{exp} (s) $ &$K_\mathrm{sat}$\\
\hline \hline
1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 & -4.0 \\
2		& Bright JWST Calibrator			& G2 V			& 6.5	  		& On &	64$\times$64	& F430M &  220 & -4.0 \\
3		& Bright JWST Calibrator			& G2 V			& 6.5  		& Off &	64$\times$64	& F430M &  0.1 & 6.2 \\
4		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 & 6.2 \\
5		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 & 12 \\
6		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 & 13.7 \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A. The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp. The saturation limit is the 80\% well depth for 2 non-destructive reads up the ramp following a reset.}
\vspace{0.05in}
\end{table}

@@

\begin{figure*}
\centering
\subfloat[Direct Imaging PSF]{
	\includegraphics[width=0.45\textwidth]{psf_direct.pdf}
	\label{fig:psfDirect}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.45\textwidth]{psf_ND.pdf}
	\label{fig:psfND}
	}
	\caption{The \texttt{webbpsf} direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop. Both images are normalized by the peak pixel value and have arbitrary array positions but the same height and width. Aperture photometry of the sources imaged through the coronograph will have to use a large aperture encompassing the 6 outer peaks or just use the central peak(s) and apply careful background subtraction. Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.}
	\label{fig:psfComparison}
\end{figure*}

@@

Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
This is a known bug in the ASIC micro-code that can affect the integration times of small subarrays.
There are sometimes unpredictable frames which will have an additional row time (so a 1/64) increase in frame time.
This could potentially decrease the flux by 1.6\% so it is a concern for flux calibration, but it is also a rare occurrence, happening for 5 frames out of 8000.
Multiple exposures and dither positions should help lessen this effect, especially if averaged with robust statistics.

>>>>

\subsection{Hectospec Observations}
We observed NGC~2420 with two fiber configurations in the Spring and Fall of 2016.
We used the 600 gpm grating (1.9 - 2.2 $\AA$ resolution element) to match with existing spectral template libraries with 3.6 $\AA$ resolution.
We selected the central wavelength to be 4800 $\AA$ which means that the wavelength coverage is about 3550 to 6050 $\AA$, which covers several import criteria for G-star classification many of which are concentrated between 4000 and 4400 $\AA$.
We obtained exposure times of 1.7 hours (Spring 2016) and 2 hours (Fall 2016).
The minimum fiber separation $\sim$20$\arcsec$ required that we observe in two configurations to increase the density of stars for which we had spectral classification.
During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for repairs and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).

@@

We normalized the raw spectra output from \texttt{HSRED} in order to pass it to a spectral rectification program \texttt{mkclass} \citep{gray2014classification}.
The first step in the normalization was to get an approximately normalized curve from the strongly curved spectrum shown in Figure \ref{fig:SpecRect}.
We fit an 8th order polynomial in log space to the flux as a function of wavelength.
It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the best-fit polynomial drops to low values and the fit can have zero crossings.
If this polynomial model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings and reduced systematics at low fluxes.
The polynomial fit is done piecewise in 3 equally spaced regions in order to model small scale curvature.

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{calspec_and_new_clust_wd.pdf}
\caption{The NIRCam saturation and sensitivities are shown as in Figure \ref{fig:JWSTcalsWideF}.
This time, we show the CALSPEC stars, G2~V open cluster stars and placeholder spectra for WD stars from \citet{narayan2016wdnetwork}.
The faint WD stars extend much farther into the NIRCam sensitivity wells than the CALSPEC and solar analog stars.}\label{fig:wideFiltWDCalspec}
\end{figure}

@@

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the MSX calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Space Experiment (MSX) calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).

@@

\begin{table}[!b]
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:conversionSteps}
\begin{tabular}{lrrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& $K_\mathrm{src}$		& ND Square		& Subarray	& Filter & t$_\mathrm{exp} (s) $ &$K_\mathrm{sat}$\\
\hline \hline
1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 & -4.0 \\
2		& Bright JWST Calibrator			& G2 V			& 6.5	  		& On &	64$\times$64	& F430M &  220 & -4.0 \\
3		& Bright JWST Calibrator			& G2 V			& 6.5  		& Off &	64$\times$64	& F430M &  0.1 & 6.2 \\
4		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 & 6.2 \\
5		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 & 12 \\
6		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 & 13.7 \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A. The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp. The saturation limit is at 80\% well depth for 2 non-destructive reads up the ramp following a reset.}
\vspace{0.05in}
\end{table}

@@

\begin{figure*}
\centering
\subfloat[Direct Imaging PSF]{
	\includegraphics[width=0.45\textwidth]{psf_direct.pdf}
	\label{fig:psfDirect}
	}
\subfloat[NGC 2506]{
	\includegraphics[width=0.45\textwidth]{psf_ND.pdf}
	\label{fig:psfND}
	}
	\caption{The \texttt{webbpsf} direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop. Both images are normalized by the peak pixel value and have arbitrary array positions but the same height and width. Aperture photometry of the sources imaged through the coronograph will have to use a large aperture encompassing the 6 outer peaks or just use the central peak(s) and apply careful background subtraction. Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.\vspace{0.05in}}
	\label{fig:psfComparison}
\end{figure*}

@@

Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
Jarron explained further on April 24, 2017.
This is a known bug in the ASIC micro-code that can affect the frame times of small subarrays.
The bug creates extra line overheads on small subarrays.
For example, for a 32$\times$32 subarray, there are sometimes 2 line overheads and sometimes 3 line overheads about $\sim$40/60 \% of the time.
Tony Magoncelli has found a way to deterministically predict when these extra frame times will occur.
However, JWST will not produce enough data in flight to deterministically predict when the extra frame times occur so you'd have to average many frames together.
For a 64$\times$ 64 subarray, there are almost always 2 line overheads.
At a rate of about 5/8000 frames of test data, there were 3 line overheads.
So, in the worst case unlucky scenario with 64$\times$64 subarray data in RAPID mode with 2 groups up the ramp, there could be an extra 1/64 or 1.6 \% increase in the slope due to the ASIC micro code.
Given that 64$\times$64 frame time is only 0.05 s long, you could easily include hundreds of frames to average out the frame time issue with almost no change in efficiency since JWST acquisition, exposure and dithering overheads would be a much larger fraction of the time.
I would estimate this would have less than 0.01\% of an effect on flux calibration.
